
% note: Other values are accepted, which can be defined in the preamble via \texmacro{DeclareCaptionSubType}.
\begin{LongTable} [
    simple                 = true ,
    theme                  = longfoot,
    caption                = {Desert key–value options},
    entry                  = {Package key–value options},
    label                  = {options},
    note{a} = {\texmacro{baselinestretch} is set to this value at the start of \code{equation}s and \ctan{amsmath} and \ctan{mathtools} environments like \code{gather}.}
] {
    colspec                = { X[1,l] X[1,l] X[1,l] } ,
    column{1}              = { font=\ttfamily } ,
    column{2}              = { font=\ttfamily } ,
    cell{1}{1}             = { font=\sffamily\bfseries } ,
    cell{1}{2}             = { font=\sffamily\bfseries } ,
}
key    &    type    &    description  \\
article-like    &    N/A    &    (meta) Chapters don't start pages and aren't included in numbering.  \\
book-like    &    N/A    &    (meta) Adds \code{twoside,openright} to geometry.  \\
bib / hide-lang    &    bool    &    Removes the language code (e.g. \textit{en.}) from each citation.  \\
bib / per-chap    &    bool    &    Each \code{MainChapter} ends with a reference section, and \texmacro{ShowBackBib} has no effect.  \\
bib / style    &    str    &    Passed to \ctan{biblatex}. E.g. \code{ieee}.  \\
border / admonition / width    &    dim    &    Thickness of admonition border.  \\
border / admonition / pad    &    dim    &    Padding inside admonition border.  \\
border / admonition / arc    &    dim    &    Curvature of admonition border.  \\
color / table / even-row    &    color    &    If \code{simple} or \code{plain} are passed to \code{Table} or \code{LongTable}, color even rows with this.  \\
color / href / cite    &    color    &    Color of parenthetical citation links.  \\
color / href / file    &    color    &    Color of embedded file links (not common).  \\
color / href / ref    &    color    &    Color of links via e.g. \texmacro{ref} and \texmacro{cref}.  \\
color / href / run    &    color    &    Color of PDF command links (not common).  \\
color / href / url    &    color    &    Color of external URL links.  \\
color / off    &    N/A    &    (meta) Disable discretionary colors, including hyperlinks and table contents.  \\
draft    &    bool    &    Passes \code{draft} to \ctan{microtype} and some other packages.  \\
font / leading    &    float (opt)    &    If empty, uses 20\% of \code{font / size}. If non-empty, an explicit leading in \code{pt} (not recommended).  \\
font / math    &    Noto | LatinModern | STIX | Bonum | Pagella | Schola | Termes | DejaVu    &    Font family for \ctan{unicode-math} via \texmacro{setmathfont}.  \\
font / mono    &    Noto | Noto/serif | Noto/serif | LatinModern | SourcePro | Plex | Cascadia    &    Font family for \ctan{fontspec} via \texmacro{setmonofont}.  \\
font / sans    &    Noto | LatinModern | SourcePro | Plex    &    Font family for \ctan{fontspec} via \texmacro{setsansfont}.  \\
font / serif    &    Noto | LatinModern | STIX | SourcePro | Plex    &    Font family for \ctan{fontspec} via \texmacro{setmainfont}.  \\
font / size    &    float    &    Font size of main text in \code{pt} (e.g. \code{11.22}). Size commands (e.g. \texmacro{small} are scaled accordingly via \ctan{fontsize}.  \\
footer / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    (meta) Sets \code{font / back / \ldots}, \code{font / front / \ldots}, and \code{font / main / \ldots}.  \\
footer / back / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    Any TeX commands (e.g. \code{\thepage}. C=center, L=left, R=right, E=even, O=odd. For back-matter.  \\
footer / front / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    Front-matter equivalent to \code{footer / back}.  \\
footer / main / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    Main-matter equivalent to \code{footer / back}.  \\
footer / clear    &    N/A    &    (meta) Clears any footer values previously listed in the key--value list (not commonly needed).  \\
glue / abstract / authors / T    &    glue    &    Glue above author list in \code{Abstract} front-matter chapter.  \\
glue / abstract / body / T    &    glue    &    Glue above abstract body.  \\
glue / abstract / title / T    &    glue    &    Glue above abstract title.  \\
glue / bib / item / :    &    glue    &    Glue between bibliography entries.  \\
glue / caption / above / B    &    glue    &    Glue below caption and above float contents for captions placed at the top (e.g. listings), excluding tables.  \\
glue / caption / main / T    &    glue    &    Glue above captions, between caption and float contents (e.g. for figures). Sets caption style \code{dez-main}.  \\
glue / caption / panel / T    &    glue    &    Glue above figure panel captions (caption style \code{dez-panel}).  \\
glue / code / rule / :    &    glue    &    Glue above (T) or below (B) the horizontal rule in listings from \ctan{minted}.  \\
glue / eqn / long / [T | B]    &    glue    &    Glue above or below equations, in general. Sets lengths \texmacro{abovedisplayskip} and \texmacro{belowdisplayskip}.  \\
glue / eqn / short / [T | B]    &    glue    &    Applies if the text is ``short". Sets lengths \texmacro{abovedisplayshortskip} and \texmacro{belowdisplayshortskip}.  \\
glue / float--float    &    glue    &    Glue between consecutive floats. Corresponds to lengths \texmacro{floatsep} and \texmacro{intextsep}.  \\
glue / float--text    &    glue    &    Glue between float and main text. Corresponds to lengths \texmacro{textfloatsep} and \texmacro{dbltextfloatsep}.  \\
glue / fnote / :    &    glue    &    Glue between foonote items.  \\
glue / fnote / paragraph / :    &    glue    &    Glue between paragraphs in the footnote list (within a single footnote item).  \\
glue / fnote-list / [T | B]    &    glue    &    Glue above/below the footnote list. Below is only used if \code{layout / fnote / place} allows placing foonotes above floats.  \\
glue / fnote-list / rule / B    &    glue    &    Glue below the footnote list rule.  \\
glue / list / long / :    &    glue    &    Glue between \texmacro{item}s in lists, enumerations, etc. with style \code{long}.  \\
glue / list / long / T    &    glue    &    Glue above a list, etc. with style \code{long}.  \\
glue / list / short / :    &    glue    &    Glue between \texmacro{item}s with no optional style argument.  \\
glue / list / short / T    &    glue    &    Glue above lists that are started with no optional style argument.  \\
glue / list-of / :    &    glue    &    Glue between items in list of figures, nomenclature, etc., excluding the TOC. (Applies to \texmacro{ShowListOfFigures}, etc.)  \\
glue / list-of / chap-group / T    &    glue    &    Glue added above items that belong to a new chapter in the list of figures and list of tables.  \\
glue / list-of / nomencl-group / T    &    glue    &    Glue added above nomenclature items that belong to a new group.  \\
glue / paragraph / :    &    glue    &    Glue between paragraphs. Applies to the vast majority of text that contains more than 1 paragraph.  \\
glue / sec / front-chap / [T | B]    &    glue    &    Glue above or below a numberless chapter (normally front matter). Glue above is used if chapters do not start pages.  \\
glue / sec / main-chap / [T | B]    &    glue    &    Equivalent of \code{glue / sec / front-chapter / [T | B]} for numbered chapters.  \\
glue / sec / main-chap / label / B    &    glue    &    Glue between the label and name of a numbered chapter heading.  \\
glue / sec / paragraph / T    &    glue    &    Glue above \code{paragraph} section level (always \textit{runin}-style).  \\
glue / sec / part / label / B    &    glue    &    Glue between label and name of a numbered part heading.  \\
glue / sec / section / [T | B]    &    glue    &    Glue above or below section headers.  \\
glue / sec / subsec / [T | B]    &    glue    &    Glue above or below subsection headers. Glue below is ignored if \code{layout / sec / subsec-runin} is true.  \\
glue / sec / subsubsec / [T | B]    &    glue    &    Glue above or below subsubsection headers. Glue below is ignored if \code{layout / sec / subsec-runin} is true.  \\
glue / table / foot / [T | B]    &    glue    &    Glue above or below \ctan{tabularray} footers and \code{dez-table} \ctan{caption}.  \\
glue / table / head / [T | B]    &    glue    &    Glue above or below \ctan{tabularray} headers.  \\
glue / thm / [T | B]    &    glue    &    (meta) Sets \code{glue / thm / *-like / [T | B]}.  \\
glue / thm / alg-like / [T | B]    &    glue    &    Glue above and below theorem-like environments using an \code{algorithm} style (see \ctan{amsthm}).  \\
glue / thm / def-like / [T | B]    &    glue    &    Glue above and below theorem-like environments using the \code{definition} style (see \ctan{amsthm}).  \\
glue / thm / proof / [T | B]    &    glue    &    Glue above and below \code{Proof} (equivalently \code{proof}).  \\
glue / thm / rem-like / [T | B]    &    glue    &    Glue above and below theorem-like environments using the \code{remark} style (see \ctan{amsthm}).  \\
glue / thm / thm-like / [T | B]    &    glue    &    Glue above and below theorem-like environments using the \code{plain} style (see \ctan{amsthm}).  \\
glue / toc / chap / T    &    glue[=1ex plus 0.1ex minus 0.025ex]    &    Glue above chapter-level entries in the TOC.  \\
glue / toc / part / T    &    glue[=5ex plus 0.5ex minus 0.125ex]    &    Glue above part-level entries in the TOC.  \\
glue / toc / section / T    &    glue[=0.2ex plus 0.02ex minus 0.005ex]    &    Glue above section-level entries in the TOC.  \\
glue / toc / subsec / T    &    glue[=0.04ex]    &    Glue above subsec-level entries in the TOC.  \\
glue / toc / subsubsec / T    &    glue[=0ex]    &    Glue above subsubsec-level entries in the TOC.  \\
header / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    (meta) See \code{footer / *}.  \\
header / back / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    See \code{footer / *}.  \\
header / front / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    See \code{footer / *}.  \\
header / main / [ C | CE | CO | L | LE | LO | R | RE | RO ]    &    any    &    See \code{footer / *}.  \\
header / clear    &    N/A    &    (meta) See \code{footer / *}.  \\
lang / extras    &    list    &    Additional languages for \ctan{babel} to load via \texmacro{babelprovide}.  \\
lang / extras+    &    list    &    (meta) Appends to \code{lang / extras}.  \\
lang / main    &    string    &    Main language for \ctan{babel}; called via \texmacro{babelprovide}.  \\
layout / chapter-page-cmd    &    any    &    Code called at the start of each chapter.  \\
layout / endnote / backrefs    &    bool    &    Pass \code{backrefs} to \ctan{enotez}.  \\
layout / fnote / align    &    left | right | center | justify    &    Footnote list alignment.  \\
layout / fnote / place    &    default | abovefloats | belowfloats | bottom | bottomfloats | bottomfootnotes    &    Dictates how to place footnote list; see \ctan{footmisc}.  \\
layout / geometry    &    keyval    &    Passed to \ctan{geometry}'s \texmacro{geometry}.  \\
layout / geometry+    &    keyval    &    (meta) Appends to \code{layout / geometry}.  \\
layout / index / col-sep    &    dim    &    Gutter between columns in the index.  \\
layout / index / cols    &    int    &    Number of columns in the index.  \\
layout / sec / subsec-runin    &    bool    &    Switch subsection level to a \textit{runin} style that flows into the text.  \\
layout / sec / subsubsec-runin    &    bool    &    Switch section level to a \textit{runin} style that flows into the text.  \\
list-of / abbrev / symbol-width    &    dim    &    Width of the column for symbols in the list of abbreviations.  \\
list-of / abbrev / theme    &    lof | description    &    Use \code{description} if some abbreviations are too long. Refer to \ctan{acro} for more info.  \\
list-of / figure / include-panels    &    bool    &    Include figure panels (subfigures) in the list of figures.  \\
list-of / float / symbol-width    &    dim    &    Width of the column for labels (e.g. \textit{1.1}) in the list of figures and list of tables.  \\
list-of / nomencl / symbol-width    &    dim    &    Width of the column for symbols in the nomenclature.  \\
list-of / thm / symbol-width    &    dim    &    Width of the column for labels (e.g. \textit{1.1}) in lists of theorem-like things.  \\
list-of / show-links    &    bool    &    Show (color) links in the list of figures, etc., normally disabled via \texmacro{HideLinks}. TOC instead uses \code{toc / show-links}.  \\
list-of / symbol-width    &    dim    &    (meta) Sets \code{list-of / * / symbol-width}.  \\
num / chap / back    &    arabic | roman | Roman | alph | Alph    &    How to number appendices (back chapters).  \\
num / chap / by    &    arabic | roman | Roman | alph | Alph    &    (meta) Numbering style for all chapters.  \\
num / chap / front    &    arabic | roman | Roman | alph | Alph    &    Numbering style for front-matter chapters.  \\
num / chap / main    &    arabic | roman | Roman | alph | Alph    &    Numbering style for main-matter chapters.  \\
num / continuous    &    N/A    &    (meta) Use continuous arabic numbering for pages, chapters, floats, equations, and theorem-like environments.  \\
num / depth    &    none | chapter | section | subsec | subsubsec | paragraph | subpar | <n>    &    Max section numbering depth.  \\
num / eqn / brackets    &    none | round | square | curly | none-bold | round-bold | square-bold | curly-bold    &    Format of equation numbers.  \\
num / eqn / by    &    arabic | roman | Roman | alph | Alph    &    Numbeirng style for equations.  \\
num / eqn / in    &    none | chapter | section | subsec | subsubsec    &    Number equations within a level, or \textit{none}.  \\
num / float / by    &    arabic | roman | Roman | alph | Alph    &    Numbering style for floats such as \code{figure}.  \\
num / float / in    &    none | chapter | section | subsec | subsubsec    &    Numbering within  \\
num / fnote / by    &    arabic | roman | Roman | alph | Alph | lamport | lamport* | bringhurst | chicago | wiley | dez-fancy    &    Numbering style for footnotes via \ctan{footmisc}.  \\
num / fnote / in    &    none | page | chapter    &    Reset footnote numbering each page or chapter, or none.  \\
num / page / back    &    arabic | roman | Roman | alph | Alph    &    Numbering style for back-matter pages.  \\
num / page / by    &    arabic | roman | Roman | alph | Alph    &    (meta) Numbering style for all pages.  \\
num / page / front    &    arabic | roman | Roman | alph | Alph    &    Numbering style for front-matter pages.  \\
num / page / main    &    arabic | roman | Roman | alph | Alph    &    Numbering style for main-matter pages.  \\
num / panel / by    &    arabic | roman | Roman | alph | Alph    &    Numbering style for figure panels.  \\
num / sec / in    &    none | chapter | section | subsec | subsubsec    &    Reset section numbering at all levels up to this one, inclusive.  \\
num / thm / by    &    arabic | roman | Roman | alph | Alph    &    Numbering style for theorem-like environments in \ctan{amsthm}. Numbering is shared between all of them.  \\
num / thm / in    &    none | chapter | section | subsec | subsubsec    &    Number \ctan{amsthm} environments with respect to this level. Numbering is shared between all of them.  \\
pad / fnote / indent    &    dim[=1em]    &    Paragraph indent in footnote list (defaults to 1em if no value is passed).  \\
pad / fnote / text    &    dim[=1em]    &    Space before footnote text (after marker) in footnote list.  \\
pad / indent    &    dim    &    Paragraph indent in most text (defaults to 1em if no value is passed).  \\
pad / sec / runin    &    dim    &    Space after \textit{runin}-style section headers (normally \code{paragraph}).  \\
pad / thm / runin    &    dim    &    Space after \textit{runin}-style \ctan{amsthm} headers.  \\
pad / toc / chap    &    dim    &    Left-margin for \textit{chapter} level in the TOC.  \\
pad / toc / paragraph    &    dim    &    Left-margin for \textit{part} level in the TOC.  \\
pad / toc / part    &    dim    &    Left-margin for \textit{paragraph} level in the TOC.  \\
pad / toc / section    &    dim    &    Left-margin for \textit{section} level in the TOC.  \\
pad / toc / subsec    &    dim    &    Left-margin for \textit{subsection} level in the TOC.  \\
pad / toc / subsubsec    &    dim    &    Left-margin for \textit{subsubsection} level in the TOC.  \\
pkg / chemfig    &    package options    &    Loads \ctan{chemfig} and enables related features.  \\
pkg / chemformula    &    package options    &    Loads \ctan{chemformula} and enables related features.  \\
pkg / chemmacros    &    package options    &    Loads \ctan{chemmacros} and enables related features.  \\
pkg / circuitikz    &    package options    &    Loads \ctan{circuitikz} (option: \code{siunitx}).  \\
pkg / cryptocode    &    package options    &    Loads \ctan{cryptocode} and patches with hooks.  \\
pkg / fontawesome5    &    package options    &    Loads \ctan{fontawesome5}, enabling those symbols.  \\
pkg / graphs    &    N/A    &    Loads \code{graphdrawing} and other \ctan{tikz} graph libraries.  \\
pkg / imakeidx    &    package options    &    Loads \ctan{imakeidx}, enabling \texmacro{ShowIndex}.  \\
pkg / kantlipsum    &    package options    &    Loads \ctan{kantlipsum} and enables \texmacro{NextKant} and \texmacro{RandKant}.  \\
pkg / knowledge    &    package options    &    Loads \ctan{knowledge}. (Note: loading this package after desert will not work correctly.)  \\
pkg / lettrine    &    package options    &    Loads \ctan{lettrine} for drop-caps. Currently has no other effect.  \\
pkg / minted    &    package options    &    Loads \ctan{minted}, configures the \code{listing} environment, and enables the \code{MintedCode} environment.  \\
pkg / noms    &    package options    &    Loads \code{noms} and \ctan{nomencl}, enabling \texmacro{ShowNomenclature} and nomenclature declarations.  \\
pkg / svg    &    package options    &    Loads \code{svg}. Currently has no other effect.  \\
pkg / tcolorbox    &    package options    &    Loads \code{tcolorbox}, enabling admonitions via \texmacro{NewAdmonitionEnv}, etc.  \\
pkg / tikz    &    N/A    &    Loads \ctan{tikz} and various extra packages.  \\
pkg / tikz-cd    &    package options    &    Loads \ctan{tikz-cd} for commutative diagrams. Currently has no other effect.  \\
pkg / ulem    &    package options    &    Loads \ctan{ulem} and enables underlining, strike-through, etc. in \code{textiles}.  \\
pkg / varioref    &    package options    &    Loads \ctan{varioref}. (Note: Loading this package after desert will not work correctly.)  \\
preset / Berkeley    &    N/A    &    (meta) Preset for PhD dissertations at UC Berkeley.  \\
preset / Cambridge    &    N/A    &    (meta) Preset for PhD dissertations at Cambridge.  \\
preset / Chicago    &    N/A    &    (meta) Preset for PhD dissertations at U Chicago.  \\
preset / CMU    &    N/A    &    (meta) Preset for PhD dissertations at Carnegie Mellon.  \\
preset / generic-A4    &    N/A    &    (meta) Preset with simple A4 geometry.  \\
preset / generic-letterpaper    &    N/A    &    (meta) Preset with simple letter-paper geometry.  \\
preset / Harvard    &    N/A    &    (meta) Preset for PhD dissertations at Harvard.  \\
preset / Stanford    &    N/A    &    (meta) Preset for PhD dissertations at Stanford.  \\
preset / UCL    &    N/A    &    (meta) Preset for PhD dissertations at University College London.  \\
preset / UCSD    &    N/A    &    (meta) Preset for PhD dissertations at UC San Diego.  \\
preset / UCSF    &    N/A    &    (meta) Preset for PhD dissertations at UC San Francisco.  \\
rule / fnote-list    &    dim    &    Thickness of footnote rule.  \\
rule / fnote-list / width    &    dim    &    Horizontal length of footnote rule. Set to 0 to disable or negative for \texmacro{textwidth}.  \\
rule / page / footer    &    dim    &    Thickness of page footer rule. Set to 0 to disable.  \\
rule / page / header    &    dim    &    Thickness of page header rule. Set to 0 to disable.  \\
rule / table / border    &    dim    &    Thickness of rule above and below tables if \code{simple} or \code{plain} is passed.  \\
rule / table / extra    &    dim    &    Intended for rules in only some table cells. Currently not used directly.  \\
rule / table / top-row    &    dim    &    Thickness of rule below the header row of a table if \code{simple} is passed.  \\
stretch / bib    &    float    &    Line spacing in bibliography.  \\
stretch / caption    &    float    &    Line spacing in captions and table footers.   \\
stretch / code    &    float    &    Line spacing in \ctan{minted} source code.  \\
stretch / double    &    N/A    &    (meta) Sets most spacing to 1.66667 (baseline-distance=2*x-height); captions, bibliography, code, and tables to 1.0.  \\
stretch / eqn    &    float    &    Line spacing in equations. \TblrNote{a}  \\
stretch / list-of    &    float    &    Line spacing in list of figures, nomenclature, etc., excluding TOC.  \\
stretch / main    &    float    &    Line spacing in the main text.  \\
stretch / one-half    &    N/A    &    (meta) Sets most spacing to 1.25 (baseline-distance=1.5*x-height); captions, bibliography, code, and tables to 1.0.  \\
stretch / quote    &    float    &    Line spacing in display-style quotations via \ctan{csquotes}, the \texmacro{Quote} command, and the \code{Quotation} environment.  \\
stretch / single    &    N/A    &    (meta) Sets all spacing to 1.25 (baseline-distance=1.0*x-height).  \\
stretch / table    &    float    &    Line spacing in \ctan{tabularray} table contents.  \\
stretch / toc    &    float    &    Line spacing in the TOC.  \\
style / abstract / authors    &    style (unary)    &    Text style in the \code{Abstract} environment's author list (\textit{author} in \texmacro{SetInfo}).  \\
style / abstract / by    &    style (unary)    &    Style in the \code{Abstract} environment's line between the title and author list (normally ``by" in English).  \\
style / abstract / title    &    style (unary)    &    Style in the \code{Abstract} environment's thesis/article title (\textit{title} in \texmacro{SetInfo}).  \\
style / admonition / label    &    style (unary)    &    Style of an admonition's label (e.g. \textit{Warning} or a symbol).  \\
style / admonition / name    &    style (unary)    &    Style of an admonition's name passed via \code{name=}.  \\
style / caption / body    &    style (unary)    &    (meta) Sets \code{style/caption/main/body},  \code{style/caption/above/body}, and  \code{style/caption/top/body}.  \\
style / caption / entry    &    style (unary)    &    Style for the entry with \code{caption+}. Applied on top of the relevant \code{style/caption/*/body} key.  \\
style / caption / label    &    style (unary)    &    (meta) Sets \code{style/caption/main/label},  \code{style/caption/above/label}, and  \code{style/caption/top/label}.  \\
style / caption / above / body    &    style (unary)    &    Style of the caption body for captions above, not including tables.  \\
style / caption / above / label    &    style (unary)    &    Style of the caption label and separator for captions above, not including tables.  \\
style / caption / main / body    &    style (unary)    &    Style of caption body for captions below.  \\
style / caption / main / label    &    style (unary)    &    Style of caption label and separator for captions below.  \\
style / caption / panel / body    &    style (unary)    &    Style of caption body for figure panels.  \\
style / caption / panel / label    &    style (unary)    &    Style of caption label and separator for figure panels.  \\
style / caption / subref    &    style (unary)    &    Style of referenced panel labels from inside a figure's caption.  \\
style / chemfig / figure    &    style (math)    &    Math code applied to \ctan{chemfig} per call.  \\
style / chemfig / name    &    style (unary)    &    Style of name in \ctan{chemfig} \texmacro{chemname}.  \\
style / code / line-num    &    style (nullary)    &    Style of line numbers via \ctan{minted}.  \\
style / code / source    &    style (nullary)    &    Style of code via \ctan{minted}.  \\
style / fnote / body    &    style (nullary)    &    Style of footnotes (in the list).  \\
style / indexed-starred    &    style (unary)    &    Style for \texmacro{indexed*}.  \\
style / list-of / nomencl-group    &    style (unary)    &    Style for subheadings in the nomenclature (e.g. \textit{Greek symbols}).  \\
style / sec / front-chap    &    style (nullary)    &    Style of numberless chapter headings, typically reserved for front matter.  \\
style / sec / main-chap / label    &    style (nullary)    &    Style of the chapter label (e.g. \textit{chapter 1}) in numbered chapters.  \\
style / sec / main-chap / name    &    style (nullary)    &    Style of the chapter name in numbered chapters.  \\
style / sec / paragraph    &    style (nullary)    &    Style of a runin paragraph-level section.  \\
style / sec / part / label    &    style (nullary)    &    For \textit{part} section level.  \\
style / sec / part / name    &    style (nullary)    &    For \textit{part} section level.  \\
style / sec / section    &    style (nullary)    &    For \textit{subsec} section level.  \\
style / sec / subsec    &    style (nullary)    &    For \textit{subsec} section level.  \\
style / sec / subsubsec    &    style (nullary)    &    For \textit{subsubsec} section level.  \\
style / table / foot    &    style (nullary)    &    Style of the table footer, including notes and remarks.  \\
style / table / head / body    &    style (nullary)    &    Style of the table header's body, equivalent to a caption body.  \\
style / table / head / label    &    style (nullary)    &    Style of the table header's label (e.g. \textit{Table 1.1}) and separator, equivalent to a caption body.  \\
style / tikz    &    style (nullary)    &    Text style applied at the start of every \ctan{tikz} diagram.  \\
style / toc / chap    &    style (nullary)    &    Style applied to chapter-level line in the TOC.  \\
style / toc / chap / label    &    style (nullary)    &    Style applied to chapter-level line in the TOC.  \\
style / toc / page-num    &    style (nullary)    &    Style applied to the chapter's label (e.g. \textit{1}) in the TOC, added on top of \code{style / toc / chap}.  \\
style / toc / part    &    style (nullary)    &    For \textit{part} section level.  \\
style / toc / part / label    &    style (nullary)    &    For \textit{part} section level.  \\
style / toc / section    &    style (nullary)    &    For \textit{section} section level.  \\
style / toc / section / label    &    style (nullary)    &    For \textit{section} section level.  \\
style / toc / subsec    &    style (nullary)    &    For \textit{subsection} section level.  \\
style / toc / subsec / label    &    style (nullary)    &    For \textit{subsection} section level.  \\
style / toc / subsubsec / label    &    style (nullary)    &    For \textit{subsubsection} section level.  \\
style / toc / subsubsec    &    style (nullary)    &    For \textit{subsubsection} section level.  \\
toc / depth    &    none | chapter | section | subsec | subsubsec | paragraph | <n>    &    Max depth at which to show levels in the TOC.  \\
toc / bib    &    bool    &    Include any bibliography sections in the TOC.  \\
toc / endnotes    &    bool    &    Include any endnotes sections in the TOC.  \\
toc / index    &    bool    &    Include the index in the TOC.  \\
toc / show-links    &    bool    &    Show links in the TOC, normally disabled with \texmacro{HideLinks} .  \\
typo / admonition / label-sep    &    any    &    Characters between admonition labels and names if a name is passed.  \\
typo / caption / label-sep    &    any    &    Characters between a caption's label (e.g. \textit{Figure 1.1}) and its body.  \\
typo / caption / subref / format    &    any    &    Format of panel references inside a caption (e.g. \textit{1a}). Sets \texmacro{subrefformat} in \ctan{subcaption}.  \\
typo / caption / subref / label-sep    &    plain | parens    &    Characters between a panel reference inside a caption and a description in \texmacro{describepanels}.  \\
typo / hyphens-off    &    bool    &    Sets all hyphenation penalties to infinite, preventing TeX from breaking words over lines via hyphenation.  \\
typo / quote / max-lines    &    int    &    Switch to quote display style after this number of lines. Refer to \ctan{csquotes}.  \\
typo / ref / abbreviate    &    bool    &    Passes \code{abbreviate} to \ctan{cleveref} (e.g. \textit{fig.} instead of \textit{figure}).  \\
typo / ref / capitalize    &    bool    &    Passes \code{capitalize} to \ctan{cleveref} (e.g. \texmacro{cref} behaves like \texmacro{Cref}).  \\
typo / siunitx / extra    &    keyval    &    Extra key--value pairs to pass to \ctan{siunitx} via \texmacro{sisetup}.  \\
typo / siunitx / extra+    &    keyval    &    (meta) Appends to \code{typo / siunitx / extra}.  \\
typo / siunitx / group    &    none | all | decimal | integer    &    Passed to \ctan{siunitx} via \texmacro{sisetup} to group digits. (Note: Desert references this.)  \\
typo / siunitx / mode    &    match | math | auto    &    Whether \ctan{siunitx} should always use math mode (\code{math}) or keep the active mode and style (\code{match}).  \\
typo / table / note / label-sep    &    any    &    Characters between \ctan{tabularray} note labels and text.  \\
typo / table / remark / label-sep    &    any    &    Characters between \ctan{tabularray} remark labels and text.  \\
\end{LongTable}



\begin{LongTable} [
    simple                 = true ,
    theme                  = longfoot ,
    entry                  = {Packages loaded by Desert} ,
    caption+               = { (some optional)} ,
    label                  = {packages} ,
]{
    colspec                = { X[2,l] X[1,l] X[2,l] } ,
    column{1}              = { font=\ttfamily } ,
    column{2}              = { font=\ttfamily } ,
    cell{1}{1}             = { font=\sffamily\bfseries } ,
    cell{1}{2}             = { font=\sffamily\bfseries } ,
}
name                        & options              & purpose                      \\
\ctan{accsupp}              &                      & before: acro                 \\
\ctan{acro}                 &                      & for all abbreviations        \\
\ctan{adjustbox}            &                      & resize boxes                 \\
\ctan{amsthm}               &                      & theorem envs                 \\
\ctan{babel}                & <langs>              & language                     \\
\ctan{biblatex}             & backend=biber        & (after: hyperref)            \\
\ctan{caption}              & hypcap=true          & caption setup                \\
\ctan{chemfig}              &                      & chemical diagrams            \\
\ctan{chemformula}          &                      &                              \\
\ctan{chemmacros}           &                      &                              \\
\ctan{cleveref}             &                      & \texmacro{cref}                 \\
\ctan{crossreftools}        &                      &                              \\
\ctan{cryptocode}           &                      & lots of CS envs              \\
\ctan{csquotes}             &                      & quotation envs               \\
\ctan{csvsimple-l3}         &                      & tables from CSV files        \\
\ctan{datetime2}            &                      & format dates                 \\
\ctan{ellipsis}             &                      & fix \texmacro{ldots}            \\
\ctan{enotez}               &                      & fixed endnotes               \\
\ctan{enumitem}             &                      & control spacing for lists    \\
\ctan{fancyhdr}             &                      & footer and header            \\
\ctan{fancyvrb}             &                      & better \texmacro{verb}          \\
\ctan{fnpct}                &                      & fnote marks position         \\
\ctan{fontawesome5}         &                      &                              \\
\ctan{fontsize}             &                      & more font size commands  \\
\ctan{fontspec}             &                      & all font loading             \\
\ctan{footmisc}             &                      & fnote style and counters     \\
\ctan{fvextra}              &                      & improves fancyvrb            \\
\ctan{geometry}             &                      & \texmacro{geometry}             \\
\ctan{glue}                 &                      & rubber-preserving calc       \\
\ctan{graphicx}             &                      & \texmacro{includegraphics}      \\
\ctan{hyperref}             &                      & (after xindy+geometry)       \\
\ctan{hyperxmp}             &                      & XMP metadata                 \\
\ctan{imakeidx}             & xindy                & index (before knowledge)     \\
\ctan{info}                 &                      & save/format data; set XMP    \\
\ctan{knowledge}            &                      &                              \\
\ctan{lscape}               &                      & \code{landscape} env         \\
\ctan{lua-widow-control}    &                      & needs Tex Live 2022          \\
\ctan{lualatex-math}        &                      & math-related patches         \\
\ctan{mathcommand}          &                      & prime+subscript-aware        \\
\ctan{mathtools}            &                      & declare theorem envs         \\
\ctan{microtype}            & babel=true           &                              \\
\ctan{minted}               & newfloat             & color source code            \\
\ctan{newfloat}             &                      & declare float envs           \\
\ctan{nomencl}              &                      & nomenclature                 \\
\ctan{noms}                 &                      & nomencl groups and utils     \\
\ctan{pdflscape}            &                      & makes \ctan{lscape} rotate in PDF \\
\ctan{perpage}              &                      & reset counter per page       \\
\ctan{pidgin}               &                      & language                     \\
\ctan{ragged2e}             & newcommands          & full ragged envs             \\
\ctan{semantic}             &                      & academic links, etc.         \\
\ctan{setspace}             &                      & loaded and then patched over \\
\ctan{showframe}            &                      & if draft                     \\
\ctan{siunitx}              &                      & typeset quantities           \\
\ctan{subcaption}           & hypcap=true          & subcaptions                  \\
\ctan{svg}                  &                      & \texmacro{includesvg}        \\
\ctan{tabularx}             &                      & for special envs only        \\
\ctan{tarmac}               &                      & internal utils               \\
\ctan{tcolorbox}            & xparse               & frame content                \\
\ctan{textiles}             & faces                &                              \\
\ctan{thmtools}             &                      & \texmacro{declaretheorem}    \\
\ctan{tikz}                 &                      & diagrams                     \\
\ctan{titlesec}             & explicit             & section formatting           \\
\ctan{titletoc}             &                      & TOC formatting               \\
\ctan{tocloft}              & titles               & do not use                   \\
\ctan{tracklang}            &                      &                              \\
\ctan{translations}         &                      &                              \\
\ctan{unicode-math}         &                      & math fonts, unicode chars    \\
\ctan{uspace}               &                      & Unicode space chars          \\
\ctan{varioref}             &                      & \texmacro{vref}              \\
\ctan{xcolor}               &                      &                              \\
\end{LongTable}


\begin{LongTable} [
    simple                 = true ,
    theme                  = longfoot ,
    entry                  = {List of Desert commands} ,
    caption+               = {} ,
    label                  = {commands} ,
]{
    colspec                = { X[2,l] X[2,l] X[2,l] } ,
    column{1}              = { font=\ttfamily } ,
    column{2}              = { font=\ttfamily } ,
    cell{1}{1}             = { font=\sffamily\bfseries } ,
    cell{1}{2}             = { font=\sffamily\bfseries } ,
}
command                     & options                    & description             \\
SetNomGroups                & \{str=str\}              &                        \\
PutConceptualNomGroups      &                          &                        \\
PutSyntacticNomGroups      &                          &                        \\
NomText                     & (str) [str] \{str\} \{str\} <str>                  &        \\
NomMath                     & (str) [str] \{str\} \{str\} <str>                   &      \\
NomUnit                     & (str) [str] \{str\} \{str\} <str>               &           \\
SetInfo                     & \{str=str\}              &                         \\
PutInfo                     & \{str=str\}              &                         \\
ProvideInfo                 & \{str=str\}              &                         \\
RemoveInfo                  & \{str\}                  &                         \\
NewInfo                     & \{str=str\}              &                         \\
RenewInfo                   & \{str=str\}              &                         \\
AddPdfDictData              &                           & adds non-\ac{XMP} to pdfinfo \\
AddPdfHyperxmpData          &                           & called automatically     \\
getinfo                     & \{str\} [K–V]               &                         \\
GetInfo                     & \{str\} [K–V]               & sentence-case variant   \\
infolist                    & \{str\} [K–V]               &                         \\
InfoList                    & \{str\} [K–V]               & sentence-case variant   \\
InfoInline                  & \{str\} [K–V]             & format inline data  \\
InfoListInline              & \{str,\ldots\} [K–V]        & format inline list data  \\
InfoListInline              & \{str,\ldots\} [K–V]        & format inline list data  \\
TarmacSetup                 & [K–V]                      & not normally needed \\
SetTexParams                & \{macro=fp\}               & Set basic Tex params like penalties \\
SetTexPenalties             & \{str=fp\}                 & \texmacro{SetTexParams} but appends \code{penalty} to each \\
SemanticSetup               & [K–V]                     & semantic.sty \\
PidginMainLang              &                             & Get the main ``language" (dialect) \\
PidginMainBase              &                             & Base of the main language (e.g. \term{english} \\
Part                        & * [K–V] \{str\}            &                       \\
Chapter                     & * [K–V] \{str\}            &                       \\
Section                     & * [K–V] \{str\}            &                       \\
Subsection                  & * [K–V] \{str\}            &                       \\
Subsubsection               & * [K–V] \{str\}            &                       \\
Paragraph                   & * [K–V] \{str\}            &                       \\
Subparagraph                & * [K–V] \{str\}            &                       \\
SetBabelStrings             & \{str=str\}               &                         \\
SetCrefStrings              & \{str=str/str\}       &                         \\
SetTranslationStrings       & \{str=str\}               &                         \\
ProvideTranslations         & \{str=str\}              & for packages; probably not needed \\
SetBiblatexStrings          & \{str=str\}               &                         \\
Aligning                    & \{str\}                   &                        \\
LoadFrontDocs               & \{file,\ldots\}                  & \\
LoadMainDocs                & \{file,\ldots\}                  & \\
LoadBackDocs                & \{file,\ldots\}                  & \\
LoadFrontSubdocs            & \{file,\ldots\}                  & if using \ctan{subfile} \\
LoadMainSubdocs             & \{file,\ldots\}                  & if using \ctan{subfile} \\
LoadBackSubdocs             & \{file,\ldots\}                  & if using \ctan{subfile} \\
StartSubFiles               &                           & loads \ctan{subfiles} \\
LoadBib                     & \{file\}                   & just \texmacro{addbibresource} \\
LoadTex                     & \{file\}                   & just \texmacro{input} \\
DeclareDezPageStyle         & \{pagestyle\} \{hdr\} \{ftr\}  &   \\
NewFrontChapter             & \{env\} [K–V]          & make new environment \\
DeclareFrontChapter         & \{env\} [K–V]          & make environment \\
NewAppendix                 & \{env\} [K–V]          & make new environment \\
DeclareAppendix             & \{env\} [K–V]          & make environment \\
NewSpecialChapter           & \{env\} [K–V]          & make new environment \\
DeclareSpecialChapter       & \{env\} [K–V]          & make environment \\
AbstractHeader              &                            &  \\
TitleContents               &                            & title page contents \\
ShowTitle                   &                            & renders title page \\
StartChapter                & [K–V] \{str\}              & alternative to env \\
EndChapter                  &                            &  \\
StartFrontMatter            &                            & normally not needed \\
StartMainMatter             &                            & normally not needed \\
StartBackMatter             &                            & normally not needed \\
ShowBackBib                 &                            & not normally needed \\
ShowFullBib                 &                            & not normally needed \\
ShowSubBib                  &                            & not normally needed \\
ShowEndNotes                &                            & not normally needed \\
ShowIndex                   &                            & \\
NewTheoremEnv               & \{env\} [K–V]             & Calls \ctan{thmtools} \texmacro{declaretheorem} \\
DeclareTheoremStyle         & \{str\} [K–V]             & \texmacro{declaretheoremstyle} with defaults \\
NewDefaultTheoremEnvs       &                            & \\
ShowTableOfContents         &                            & \\
ShowListOfFigures           & + !                        & \\
ShowListOfTables            & + !                        & \\
ShowListOfAbbreviations     & + !                        & \\
ShowNomenclature            & + !                        & \\
ShowListOfTheoremLike       & + ! \{K–V\}               & \\
ShowListOfResults           & + ! \{K–V\}               & \ctan{thmtools} lemma, etc. (no conjecture) \\
ShowListOfAlgorithms        & + ! \{K–V\}               & thmtools ``algorithm" only \\
ShowListOfExamples          & + ! \{K–V\}               & thmtools ``example" only \\
ShowListOfDefinitions       & + ! \{K–V\}               & thmtools ``definition" only \\
ShowListOfCode              & + !                        & \\
NewListOfNewfloatCmd        & \{cmd\} \{str\}            & New listing command for float of name \code{str} \\
NewListOfCmd                & \{cmd\} \{macro\}          & Calls \code{macro} with args when \code{cmd} is called \\
indexed                     & * \{str\} [index-key]      & \\
Indexed                     & * \{str\} [index-key]      & sentence-case variant \\
captioning                  & [K–V] \{str\}             & swap-in for \texmacro{caption} \\
Caption                     & \{K–V\}                   & K–V-only \texmacro{captioning} \\
AddPanel                    & [K–V]                     & for \code{MutliPanelFigure} \\
AddPhantomPanel             & (str) \{chemfig\}          & for \code{MutliPanelFigure} \\
Chem                        & [K–V]                     & simple structural formula (no figure) \\
describepanels              & \{label-list\} \{str\}      & \\
panels                      & \{label-list\}              & multiple \texmacro{subref} \\
NewAdmonitionEnv            & [K–V] \{env\}               & \\
DeclareAdmonitionEnv        & [K–V] \{env\}               & \\
DeclareDezFloat             & \{env\} \^macro\^ \$macro\$  & uses \ctan{newfloat} and makes a wrapper env \\
LoadSourceCode              & [K–V] file                 & loads if minted \\
reffull                     & \{cite-key\}               & full reference text \\
Quote                       & [K–V] \{text\}              & Key–value \ctan{csquotes} \\
reftitle                    & \{cite-key\}                 & \\
refdoi                      & \{cite-key\}                 & \\
refurl                      & \{cite-key\}                 & \\
NextKant                    & [int]                        & next \term{n} \ctan{kantlipsum} \\
RandKant                    & [int]                        & \term{n} random \ctan{kantlipsum} \\
SetCounterWithin            & \{cntr\} \{cntr\}      & better \texmacro{counterwithin}  \\
KnowledgeSetup              & \{K–V\}                     & \texmacro{knowledgeconfigure} \\
MicrotypeSetup              & \{K–V\}                     & \texmacro{microtypesetup} \\
UnimathSetup                & \{K–V\}                     & \texmacro{unimathsetup} \\
DtmSetup                    & \{K–V\}                     & \texmacro{DTMsetup} \\
SiSetup                     & \{K–V\}                     & \texmacro{sisetup} \\
HyperSetup                  & \{K–V\}                     & \texmacro{hypersetup} \\
AcroSetup                   & \{K–V\}                     & \texmacro{acsetup} \\
CaptionSetup                & [str] \{K–V\}               & \texmacro{captionsetup} \\
TikzSetup                   & \{K–V\}                     & \texmacro{tikzset} \\
CircuitzSetup               & \{K–V\}                     & \texmacro{ctikzset} \\
MintedSetup                 & \{K–V\}                     & \texmacro{setminted} \\
GeometrySetup               & \{K–V\}                     & \texmacro{geometry} \\
ChemformulaSetup            & \{K–V\}                     & \texmacro{setchemformula} \\
ListSetup                   & [str] \{K–V\}               & \texmacro{setlist} \\
FnpctSetup                  & \{K–V\}                     & \ctan{fnpct} \\
LwcSetup                    & \{K–V\}                     & \ctan{lua-widow-control} \\
ChemSetup                   & \{K–V\}                     & \texmacro{chemsetup} \\
ChemfigSetup                & [float] \{K–V\}             & \code{setchemfig} with opt scaling \\
NomsSetup                   & \{K–V\}                     & \\
DeclareCharFallback         & \{char\} \{code\}            & replace \code{char} with \code{code} if \code{char} is unmapped \\
\end{LongTable}


\begin{LongTable} [
    simple                 = true ,
    theme                  = longfoot ,
    entry                  = {List of Desert environments} ,
    caption+               = { (some require optional packages)} ,
    label                  = {environments} ,
]{
    colspec                = { X[2,l] X[1,l] X[2,l] } ,
    column{1}              = { font=\ttfamily } ,
    column{2}              = { font=\ttfamily } ,
    cell{1}{1}             = { font=\sffamily\bfseries } ,
    cell{1}{2}             = { font=\sffamily\bfseries } ,
}
environment                 & options                          & description           \\
FrontChapter                & [K–V] \{str\}                    &                       \\
SpecialChapter              & [K–V] \{str\}                    &                       \\
MainChapter                 & [K–V] \{str\}                    &                       \\
Appendix                    & [K–V] \{str\}                    &                       \\
Appendices                  &                                   & does nothing yet      \\
Equation                    & * [K–V]                          & wrapper to \code{equation} \\
Proof                       &                                  & alias for \code{proof} (renewed amsmath env)      \\
OnePanelFigure              & * [K–V]                           &                        \\
MultiPanelFigure            & * [K–V]                           &                        \\
PhantomPanelFigure          & * [K–V]                           &                        \\
Table                       & [K–V] \{K–V\}                    & \code{talltblr} inside \code{table} \\
LongTable                   & [K–V] \{K–V\}                    & \code{longtblr} \\
SourceCode                  & [K–V]                             & \code{MintedCode} uses this \\
MintedCode                  & [K–V]                             & verbatim env \\
ChemFigure                  & [K–V]                             & needs \ctan{chemfig} \\
Where                       &                                    & table of terms inside eq \\
Quotation                   & [K–V]                             & all \ctan{csquotes} rolled into one \\
FullPage                    & [K–V]                             & use full page \\
Align                       & \{str\}                            & \\
Preface                     & [K–V]                             & a \code{FrontChapter} \\
Acknowledgments             & [K–V]                             & a \code{FrontChapter} \\
Contributions               & [K–V]                             & a \code{FrontChapter} \\
Abstract                    & [K–V]                             & a \code{FrontChapter} \\
Epigraph                    & [K–V]                             & a \code{SpecialChapter} \\
Dedication                  & [K–V]                             & a \code{SpecialChapter} \\
Copyright                   & [K–V]                             & a \code{SpecialChapter} \\
Title                       & [K–V]                             & a \code{SpecialChapter} \\
Errata                      & [K–V]                             & an \code{Appendix} \\
\textit{<admonition>}
       (e.g. \texttt{Hint}) & [K–V]              & \\
\end{LongTable}


\begin{LongTable} [
    simple                 = true ,
    theme                  = shortfoot ,
    entry                  = {List of Desert hooks} ,
    caption+               = {} ,
    label                  = {hooks} ,
]{
    colspec                = { X[3,l] X[1,l] } ,
    column{1}              = { font=\ttfamily } ,
}
hook name                     & description \\
dez / before                    &  \\
dez / after                     &  \\
dez / packages / before        &  \\
dez / packages / after        &  \\
dez / front-matter / early        &  \\
dez / front-matter / late        &  \\
dez / main-matter / early        &  \\
dez / main-matter / late        &  \\
dez / back-matter / early        &  \\
dez / back-matter / late        &  \\
dez / lof-like / before       &  \\
dez / lof-like / pre       &  \\
dez / lof-like / post       &  \\
dez / lof-like / after       &  \\
dez / show-bib / before       &  \\
dez / show-bib / pre       &  \\
dez / show-bib / post       &  \\
dez / show-bib / after       &  \\
dez / show-endnotes / before       &  \\
dez / show-endnotes / pre       &  \\
dez / show-endnotes / post       &  \\
dez / show-endnotes / after       &  \\
\end{LongTable}



\begin{LongTable} [
    simple ,
    theme                    = longfoot ,
    entry                    = {Keys to SpecialChapter} ,
    caption+                 = {} ,
    label                    = {specialchapter} ,
]{
    colspec                = { X[1,l] X[1,l] X[1,l] } ,
    column{1}              = { font=\ttfamily } ,
    column{2}              = { font=\ttfamily } ,
}
key                      & type                          & description                             \\
label                    & str                           & \texmacro{label}                            \\
entry                    & str                           & TOC entry                                \\
title                    & str                           & Title displayed as \texmacro{chapter}        \\
no-title                 & bool                          & Force-hide title                         \\
no-entry                 & bool                          & Forcibly hide TOC entry                   \\
numberless               & bool                          & Use \texmacro{chapter*} instead of \texmacro{chapter} (initial: true)   \\
numbered                 & bool                          & Force \code{numberless=false}        \\
hide-links               & bool                          & Disable link color in body        \\
empty-page-style         & bool                          & \code{pagestyle} to \code{empty}, disabling footer and header \\
width                    & h-dim                         & Width of the environment text        \\
above                    & v-dim                         & Padding from top         \\
below                    & v-dim                         & Padding from bottom         \\
textile                  & textile                       & Named textile for body         \\
style                    & style                         & Inline textile commands (e.g. \code{bold;sans})         \\
align                    & {left,center,right,justify}  & Of body         \\
at                       & {top,middle,bottom}  & Of body         \\
\end{LongTable}
